### 2014-02-22 paper/retrofit.tex
fork you

\and
\inferrule[I-fork]
{ 
|iS' = iS [ id' mapsto nil ]|\\
|tS' = q(tS)|\\
|fresh (id')|
}
{|
iconf iS (lconf id il tS (iniE (fork ie)), ldots)
.->
iconf iS' (lconf id il tS (iniE id'), ldots, lconf id' il tS' (TI ie))
|}
%{|fresh (id')|}

>>>>

\and
\inferrule[I-fork]
{ 
|iS' = iS [ id' mapsto nil ]|\\
|tS' = q(tS)|\\
|fresh (id')|
}
{|
iconf iS (lconf id il tS (fork ie), ldots)
.->
iconf iS' (lconf id il tS id', ldots, lconf id' il tS' (TI ie))
|}
%{|fresh (id')|}
